### 2024-02-01 docs/projects/noj/ml.qmd
noj - rerendered book

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7943     -0.2312      0.0256      0.2059      0.8735

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.7726     0.3098     5.7220     0.0000 ***
sepal-width         0.6807     0.0824     8.2622     0.0000 ***
petal-length        0.7112     0.0700    10.1639     0.0000 ***
petal-width        -0.5768     0.1582    -3.6467     0.0004 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3230 on 96 degrees of freedom
Multiple R-squared: 0.8500,    Adjusted R-squared: 0.8453
F-statistic: 181.3338 on 4 and 96 DF,  p-value: 2.062e-39

>>>>

Residuals:
       Min          1Q      Median          3Q         Max
   -0.8908     -0.2103      0.0371      0.2256      0.8160

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.0708     0.3356     6.1706     0.0000 ***
sepal-width         0.5954     0.0889     6.6968     0.0000 ***
petal-length        0.6671     0.0715     9.3273     0.0000 ***
petal-width        -0.4532     0.1618    -2.8002     0.0062 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3363 on 96 degrees of freedom
Multiple R-squared: 0.8299,    Adjusted R-squared: 0.8246
F-statistic: 156.1599 on 4 and 96 DF,  p-value: 8.448e-37
